Proposal: Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input

### 2021-02-28 proposal/proposal.tex
rm dead code
typo: look->looks
flesh out motivation

% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

@@

% comments on proving properties of algorithms, MATLAB code, etc.

@@

To combat this, we tested a variety of blurring techniques to reduce the visual
impact of the seams. In the process, we also aimed for producing a more coherent
whole---i.e., a mosaic that look more like a true image than a tiled grid.

>>>>

@@

There are several factors that motivate our interest in this particular
algorithm, its particular implementation, and its properties.

Personally, it is a project we've already invested in, and one which we enjoy
studying.

Academically, it presents several unique opportunities. First, as far as we can
tell, there have been no studies on either termination-properties of mosaic
algorithms or of MATLAB code. Further, we have found no attempt to formalize
details of the MATLAB programming language\footnote{This may in part be due to
the proprietary, closed-source nature of MATLAB\@. Nevertheless, we hope to make
an attempt, though it must be grounded in the knowledge that any proof can only
hold if indeed the MATLAB environment faithfully implements the semantics it
claims. There are formalizations of a particular MATLAB toolkit known as
Stateflow~\cite{Hamon_2005,Hamon_2007} but none that we have found for general
MATLAB programming.}. Thus already in studying this particularly narrow problem
we have an opportunity to extend the space of studies in formal-methods and
their applications to the programmer and their programs.

Second, we as students of these formal methods lack experience in formalizing
these details about specific algorithms. The Logical Foundations
text~\cite{Pierce:SF1} has proven a great resource in learning about these
principles on small examples, and our study of \texttt{zelda-mosaic} will make
an excellent opportunity to extend our practical knowledge of the field.

Lastly, termination and its decidability has always been a study of interest to
the logician, the mathematician, and the computer scientist. From Hilbert's
\textit{Entscheidungsproblem} to Turing's Halting problem~\cite{Cook_2011}, the
world of algorithms is generally concerned with what is, indeed, computable.
While we make no attempt here to prove termination of arbitrary or even
restricted MATLAB programs (likely a Sisyphean task), we can at least attempt to
push the boundaries of the undecidable Halting problem for this specific
program.

@@

To combat this, we tested a variety of blurring techniques to reduce the visual
impact of the seams. In the process, we also aimed for producing a more coherent
whole---i.e., a mosaic that looks more like a true image than a tiled grid.
